An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/main.tex
Section for introduction, figures for methods.

\section{Introduction}

This paper makes the following contributions.
\begin{itemize}
\item An application of \zthree\ to the constraint approach and its
  corresponding evaluation.
\item A method that given a network and a property constructs a
  minimal invariant.
\end{itemize}

\input{sec_illustration}
\input{sec_preliminaries}

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
    \node[print, right=of satc] (yes) {N satisfies P};
    \node[print, below=of satc] (dontknow) {Don't know};
    \node[state, right=of yes] (end1) {END};
    \node[state, below=of dontknow] (end2) {END};

    \draw (begin) edge (c);
    \draw (c) edge (satc);
    \draw (satc) edge node[above]{NO} (yes);
    \draw (yes) edge (end1);
    \draw (satc) edge node[right]{YES} (dontknow);
    \draw (dontknow) edge (end2);
  \end{tikzpicture}
\end{center}
\caption{Diagram for Method Safety}
\label{fig:method-safety-pseudocode}
\end{figure}

\begin{figure}
\begin{algorithmic}[1]
\State $C := \mathcal C(N)$
\If {SAT$(C \cup \{\neg P\})$}
  \State \Return 'The petri net may not satisfy the property'
\Else
  \State \Return 'The petri net satisfies the property!'
\EndIf
\end{algorithmic}
\caption{Pseudocode for Method Safety}
\label{fig:method-safety-pseudocode}
\end{figure}

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                               	$C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                    	$\delta:=\Delta(A_\theta)$\\
                                    	$C:=C \cup \{\delta\}$};
  \node[print, right=of satc] (yes) {N satisfies P};
  \node[print, right=of satctheta] (dontknow) {Don't know};
  \node[state, right=of yes] (end1) {END};
  \node[state, right=of dontknow] (end2) {END};

  \draw (begin) edge (c);
  \draw (c) edge coordinate[pos=.5] (edgein) (satc);
  \draw (satc) edge node[above]{NO} (yes);
  \draw (yes) edge (end1);
  \draw (satc) edge node[right]{YES} (modelc);
  \draw (modelc) edge (satctheta);
  \draw (satctheta) edge node[above]{NO} (dontknow);
  \draw (dontknow) edge (end2);
  \draw (satctheta) edge node[right]{YES} (modelctheta);
  \draw (modelctheta.south) -- ([yshift=-0.5cm] modelctheta.south)
  -| ([xshift=-2cm] modelctheta.west) |- (edgein);
\end{tikzpicture}
\end{center}
\caption{Diagram for Method Safety by Refinement}
\label{fig:method-safety-by-refinement-diagram}
\end{figure}

\begin{figure}
\begin{algorithmic}[1]
\State $C := \mathcal C(N)$
\While {SAT$(C \cup \{\neg P\})$}
  \State $A := $Model$(C \cup \{\neg P\})$
  \State $C_\theta := $TrapConditions$(N, A)$
  \If {SAT$(C_\theta)$}
    \State $A_\theta := $Model$(C_\theta)$
    \State $\delta := \Delta(A_\theta)$
    \State $C := C \cup \{\delta\}$
  \Else
    \State \Return 'The petri net may not satisfy the property'
  \EndIf
\EndWhile
\State \Return 'The petri net satisfies the property!'
\end{algorithmic}
\caption{Pseudocode for Method Safety by Refinement}
\label{fig:method-safety-by-refinement-pseudocode}
\end{figure}

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C':=\mathcal C'(N, \neg P)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C')$};
    \node[print, right=of satc] (noinv) {No Invariant};
    \node[action, below=of satc] (inv) {$A':=\text{Model}(C')$\\
      $I := \text{Inv}(N, A')$};
    \node[print, below=of inv] (printinv) {Invariant: $I$};
    \node[state, right=of noinv] (end1) {END};
    \node[state, below=of printinv] (end2) {END};

    \draw (begin) edge (c);
    \draw (c) edge (satc);
    \draw (satc) edge node[above]{NO} (noinv);
    \draw (satc) edge node[right]{YES} (inv);
    \draw (noinv) edge (end1);
    \draw (inv) edge (printinv);
    \draw (printinv) edge (end2);
  \end{tikzpicture}
\end{center}
\caption{Diagram for Method Invariant}
\label{fig:method-invariant-diagram}
\end{figure}

\begin{figure}
\begin{algorithmic}[1]
\State $C' := \mathcal C'(N, \neg P)$
\If {SAT$(C')$}
  \State $A' := $Model$(C')$
  \State $I := $Inv$(N, A')$
  \State \Return 'Invariant I for the petri net: $I$'
\Else
  \State \Return 'Failed at finding an invariant'
\EndIf
\end{algorithmic}
\caption{Pseudocode for Method Invariant}
\label{fig:method-invariant-pseudocode}
\end{figure}

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C':=\mathcal C'(N, \neg P)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C')$};
    \node[print, right=of satc] (noinv) {No Invariant};
    \node[action, below=of satc] (model1) {$A':=\text{Model}(C')$};
    \node[action, below=of model1] (cm) {$C_M:=\text{MinConstraints}(N, A')$};
    \node[decision, below=of cm] (satcm) {$\text{SAT}(C' \cup C_M)$};
    \node[action, right=of satcm] (model2) {$A':=\text{Model}(C' \cup C_M)$};
    \node[action, below=of satcm] (inv) {$I := \text{Inv}(N, A')$};
    \node[print, below=of inv] (printinv) {Invariant: $I$};
    \node[state, right=of noinv] (end1) {END};
    \node[state, below=of printinv] (end2) {END};

    \draw (begin) edge (c);
    \draw (c) edge (satc);
    \draw (satc) edge node[above]{NO} (noinv);
    \draw (noinv) edge (end1);
    \draw (satc) edge node[right]{YES} (model1);
    \draw (model1) edge coordinate[pos=.5] (edgein) (cm);
    \draw (cm) edge (satcm);
    \draw (satcm) edge node[above]{YES} (model2);
    \draw (model2) |- (edgein);
    \draw (satcm) edge node[right]{NO} (inv);
    \draw (inv) edge (printinv);
    \draw (printinv) edge (end2);
  \end{tikzpicture}
\end{center}
\caption{Diagram for Method Invariant with Minimization}
\label{fig:method-invariant-with-minimization-diagram}
\end{figure}

\begin{figure}
\begin{algorithmic}[1]
\State $C' := \mathcal C'(N, \neg P)$
\If {SAT$(C')$}
  \State $A' := $Model$(C')$
  \State $C_M := $MinConstraints$(N, A')$
  \While {SAT$(C' \cup C_M)$}
    \State $A' := $Model$(C' \cup C_M)$
    \State $C_M := $MinConstraints$(N, A')$
  \EndWhile
  \State $I := $Inv$(N, A')$
  \State \Return 'Invariant I for the petri net: $I$'
\Else
  \State \Return 'Failed at finding an invariant'
\EndIf
\end{algorithmic}
\caption{Pseudocode for Method Invariant with Minimization}
\label{fig:method-invariant-with-minimization-pseudocode}
\end{figure}

@@

\begin{figure}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$\\
                                        $D:=\{\}$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                                        $C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                                $\delta:=\Delta(A_\theta)$\\
                                                $C:=C \cup \{\delta\}$\\
                                                $D:=D \cup \{\delta\}$};
  \node[print, right=of satctheta] (noinv2) {No Invariant};
  \node[state, below=of noinv2] (end3) {END};

  \node[action, right=of satc] (cprime) {$C':=\mathcal C'(N, \neg P \land D)$};
  \node[decision, right=of cprime] (satcprime) {$\text{SAT}(C')$};
  \node[action, below=of satcprime] (inv) {$A':=\text{Model}(C')$\\
                                        $I:=D \land \text{Inv}(N, A')$};
  \node[print, below=of inv] (printinv) {Invariant: $I$};
  \node[print, right=of satcprime] (noinv) {No Invariant};
  \node[state, below=of noinv] (end1) {END};
  \node[state, below=of printinv] (end2) {END};

  \draw (cprime) edge (satcprime);
  \draw (satcprime) edge node[above]{NO} (noinv);
  \draw (satcprime) edge node[right]{YES} (inv);
  \draw (inv) edge (printinv);
  \draw (noinv) edge (end1);
  \draw (printinv) edge (end2);

  \draw (begin) edge (c);
  \draw (c) edge coordinate[pos=.5] (edgein) (satc);
  \draw (satc) edge node[above]{NO} (cprime);
  \draw (satc) edge node[right]{YES} (modelc);
  \draw (modelc) edge (satctheta);
  \draw (satctheta) edge node[above]{NO} (noinv2);
  \draw (noinv2) edge (end3);
  \draw (satctheta) edge node[right]{YES} (modelctheta);
  \draw (modelctheta.south) -- ([yshift=-0.5cm] modelctheta.south)
  -| ([xshift=-2cm] modelctheta.west) |- (edgein);
\end{tikzpicture}
\caption{Diagram for Method Invariant by Refinement}
\label{fig:method-invariant-by-refinement-diagram}
\end{figure}

\begin{figure}
\begin{algorithmic}[1]
\State $C := \mathcal C(N)$
\State $D := $true
\While {SAT$(C \cup \{\neg P\})$}
  \State $A := $Model$(C \cup \{\neg P\})$
  \State $C_\theta := $TrapConditions$(N, A)$
  \If {SAT$(C_\theta)$}
    \State $A_\theta := $Model$(C_\theta)$
    \State $\delta := \Delta(A_\theta)$
    \State $C := C \cup \{\delta\}$
    \State $D := D \land \delta$
  \Else
    \State \Return 'Failed at finding an invariant'
  \EndIf
\EndWhile
\State $C' := \mathcal C'(N, \neg P \land D)$
\If {SAT$(C')$}
  \State $I := D \land $Inv$(N, A')$
  \State \Return 'Invariant I for the petri net: $I$'
\Else
  \State \Return 'Failed at finding an invariant'
\EndIf
\end{algorithmic}
\caption{Pseudocode for Method Invariant by Refinement}
\label{fig:method-invariant-by-refinement-pseudocode}
\end{figure}

>>>>

\input{sec_introduction}
\input{sec_illustration}
\input{sec_preliminaries}

@@

\input{fig_dia_method_safety}

\input{fig_method_safety}

@@

\input{fig_dia_method_safety_by_refinement}

\input{fig_method_safety_by_refinement}

@@

\input{fig_dia_method_invariant}

\input{fig_method_invariant}

@@

\input{fig_dia_method_invariant_w_minimization}

\input{fig_method_invariant_w_minimization}

@@

\input{fig_dia_method_invariant_by_refinement}

\input{fig_method_invariant_by_refinement}
